Computer Science House Constitution

### 2025-09-21 constitution.tex
removed mention of co-op from Eligible Votes

@@

The following requirements must be met for an Active Member to be allowed to vote after the first Intro Evals of the academic year.
Any of these requirements may be waived by the Evals Director or an E-Board Vote.
\begin{enumerate}
	\item Attend at least six House Meetings
	\item Attend at least six directorship meetings
	\item Attend at least one CSH social event
	\item Attend at least two Technical Seminars
\end{enumerate}

@@

\asubsection{Constitutional Maintainer Selection}
Any member may nominate a qualified member for Maintainer status to E-Board for consideration.
E-Board may choose to approve or reject the nomination by E-Board Vote with a quorum of seventy-five percent.

@@

\asubsection{Eligible Votes}
The number of Active Members who are eligible to vote on the issue.
Following the first Intro Eval of the academic semester, Active Members are only eligible to vote if they have completed the qualifications listed in \ref{Expectations of Voting Members}.
Officers of CSH retain voting eligibility on all matters directly pertaining to the duties of their held office regardless of \ref{Expectations of Voting Members}.

>>>>

Active Members currently on co-op forfeit their right to vote on house issues, and likewise do not count towards quorum.
Exceptions may be made at the discretion of the Evaluations Director.

@@

The following requirements must be met by the beginning of the Intro Eval for an Active Member to be allowed to vote.
Any of these requirements may be waived by the Evals Director or an E-Board Vote.
\begin{enumerate}
	\item Attend all House Meetings during the Intro Process
	\item Attend at least one directorship meeting for each week of the Intro Process % The number of directorship meetings intended here is equal to the number of the weeks in the process, not just one each week
	\item Attend at least one CSH social event during the Intro Process
	\item Attend at least two Technical Seminars during the Intro Process
\end{enumerate}

@@

\asubsection{Constitutional Maintainer Selection}
Any member may nominate a qualified member for Maintainer status to E-Board for consideration.
E-Board may choose to approve or reject the nomination by E-Board Vote with a quorum of seventy-five percent of the Eligible Votes.

@@

\asubsection{Eligible Votes}
The number of Active Members eligible to vote on the issue.
